An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-19 paper/main.tex
update tex 20191119
add authors/change the file names of related work & conclusion

\begin{document}
%
\title{
  % Strategies for efficient composition of bidirectional programs
  % by memoization and lazy updates
  %  tupling
  %  accumulating updates = lazy updates
  %  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}  
  An efficient composition of bidirectional programs
  by memoization and lazy update
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}

%{Zhenjiang Hu\inst{1}\orcidID{0000-0002-9034-205X}}
%{Robert Gl\"{u}ck\inst{2}\orcideID{0000-0001-6990-3935}}
%{Kanae Tsushima\inst{3}\orcidID{}}
%{Bach-Trong Nguyen\inst{3}\orcidID{0000-0002-6342-6020}}
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%15--250 words.
 \input{0.abst.tex}
 % We show experimental results for several BX programs with simple inputs and large inputs.

@@

\newpage

@@

\input{7.experiments.tex}

\input{8.related-work.tex}

\input{9.conclusion.tex}

@@

% From sample code
% 
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{viewupdate}
F. Bancilhon and N. Spyratos. ``Update semantics of relational views''. ACM Transactions on Database Systems, 6(4):557--575, 1981.

@@

\input{result2.tex}

>>>>

\begin{document}
%
\title{
  % Strategies for efficient composition of bidirectional programs
  % by memoization and lazy updates
  %  tupling
  %  accumulating updates = lazy updates
  %  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}  
  An efficient composition of bidirectional programs
  by memoization and lazy update
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{{Kanae Tsushima\inst{1}\orcidID{0000-0002-3383-3389}} \and
  {Bach-Trong Nguyen\inst{1}\orcidID{0000-0002-6342-6020}} \and
  {Robert Gl\"{u}ck\inst{2}\orcidID{0000-0001-6990-3935}} \and
  {Zhenjiang Hu\inst{3}\orcidID{0000-0002-9034-205X}}}

\authorrunning{K. Tsushima et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{National Institute of Informatics, Japan
  \email{\{k\_tsushima,bach\}@nii.ac.jp} \and
  University of Copenhagen, Denmark
  \email{glueck@di.ku.dk } \and
  Peking University, China
  \email{huzj@pku.edu.cn}}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in
%15--250 words.
 \input{0.abst.tex}
 % We show experimental results for several BX programs with simple inputs and large inputs.

@@

@@

\input{5.experiments.tex}

\input{6.related-work.tex}

\input{7.conclusion.tex}

@@

% From sample code
% 
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%

\tiny

\begin{thebibliography}{8}
\bibitem{viewupdate}
F. Bancilhon and N. Spyratos. ``Update semantics of relational views''. ACM Transactions on Database Systems, 6(4):557--575, 1981.

@@
